---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mathcalculate

<!-- badges: start -->
[![R-CMD-check](https://github.com/SihanChenn/mathcalculate/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SihanChenn/mathcalculate/actions/workflows/R-CMD-check.yaml)

[![Codecov test coverage](https://codecov.io/gh/SihanChenn/mathcalculate/branch/main/graph/badge.svg)](https://app.codecov.io/gh/SihanChenn/mathcalculate?branch=main)
<!-- badges: end -->

The goal of mathcalculate is to compute linear regression models using least square method, and get a result about estimated coefficients (including estimated coefficients, standard error of estimated coefficients, t statistics and p-value) and estimated Y. Be careful that to run this package, both X and Y should not have any NA values.

This package contains two functions. "linear_regress" is to compute linear regression models and get estimated coefficients. "PredictedY" is to get predicted values for a linear regression. 

Please see help page in R package for more detailed information about these two functions.

## Installation

You can install the development version of mathcalculate from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SihanChenn/mathcalculate")
```

## Example

This is a basic example which shows you how to use this package:

```{r example}
library(mathcalculate)
#basic example code
data("mtcars")
#set up x and y
y = mtcars$mpg
x = as.matrix(mtcars[, -which(names(mtcars) == "mpg")])
#get linear regression results using linear_regress
result = linear_regress(y, x)
#get predicted values from PredictY
y_hat = PredictY(x, result[["Estimate"]])
# results
print(result)
print(y_hat)
```

Scatter plot for predicted y v.s. actual y.

```{r pressure, echo = FALSE}
plot(y_hat, y, main = "Predicted vs Actual Values", 
     xlab = "Predicted Values", ylab = "Actual Values", 
     pch = 16, col = "black")  # pch=16 creates filled circles, col=blue sets color
abline(0, 1, col = "red", lwd = 2)
```

