---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
To use the package mathcalculate:

Both the y and x should not have any NA values.
```{r setup}
library(mathcalculate)
```
Use the Boston dataset (Housing Values in Suburbs of Boston) from the MASS package to demonstrate how package mathcalculate works. The dependent variable is medv (median value of owner-occupied homes in $1000s), independent variables are other variables in Boston dataset. 
```{r}
library(MASS)
library(knitr)
data(Boston)
y=Boston$medv
x=as.matrix(Boston[, -which(names(Boston) == "medv")])
lm1=linear_regress(y,x)
y_hat=PredictY(x,lm1[["Estimate"]])
print(lm1)
```
Using original R function lm to demonstrate both correctness and the efficiency.
```{r}
lm_fit=lm(y~x)
summary_fit=summary(lm_fit)
```

Test correctness of estimated coefficients, standard errors, t-statistics, p-value.
```{r}
all.equal(lm1[["Estimate"]], coef(lm_fit), tolerance = 1e-5)
all.equal(lm1[["Std_Err"]], summary_fit$coefficients[, "Std. Error"], tolerance = 1e-5)
all.equal(lm1[["t_statistic"]],summary_fit$coefficients[, "t value"], tolerance = 1e-5)
all.equal(lm1[["p_value"]], summary_fit$coefficients[, "Pr(>|t|)"], tolerance = 1e-5)
all.equal(y_hat, predict(lm_fit), tolerance = 1e-5)
```
Test efficiency.
```{r}
benchmark_results <- bench::mark(
  mathcalclate = {
    lm1 <- linear_regress(y, x)
    y_hat <- PredictY(x, lm1[["Estimate"]])
    list(Estimate = lm1[["Estimate"]],Std_Err = lm1[["Std_Err"]],t_statistic =lm1[["t_statistic"]], p_value = lm1[["p_value"]],y_hat = y_hat)},
  # Base R linear regression
  base = {
    lm_fit <- lm(y ~ x)
    summary_fit <- summary(lm_fit)
    list(Estimate = coef(lm_fit),Std_Err = summary_fit$coefficients[, "Std. Error"],t_statistic = summary_fit$coefficients[, "t value"],p_value = summary_fit$coefficients[, "Pr(>|t|)"],y_hat = predict(lm_fit))},
  check = function(mathcalclate, base) {
    is_equal <- all(
      all.equal(mathcalclate[["Estimate"]], base[["Estimate"]], tolerance = 1e-5),
      all.equal(mathcalclate[["Std_Err"]], base[["Std_Err"]], tolerance = 1e-5),
      all.equal(mathcalclate[["t_statistic"]], base[["t_statistic"]], tolerance = 1e-5),
      all.equal(mathcalclate[["p_value"]], base[["p_value"]], tolerance = 1e-5),
      all.equal(mathcalclate[["y_hat"]], base[["y_hat"]], tolerance = 1e-5)
    )
    if (!is_equal) stop("Results do not match.")
    is_equal
  }
)
# Print the benchmark results
print(benchmark_results)

```
